%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {IT Operations Specialist} % Job title
    {SCAN Health Plan} % Organization
    {Long Beach, CA, U.S.} % Location
    {Jul. 2024 - May. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Drove endpoint compliance with Sec/Net/Systems Eng. departments for HIPAA–aligned baselines; documented remediations and exceptions.}
        \item {automated user life cycle and administration tasks with PowerShell/Python and AAD/Exchange APIs; reduced manual effort and error rate.}
        \item {Built asset and patch reports from Lansweeper asset management database; improved cross-team visibility for audits and change reviews.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Asset Management Technician} % Job title
    {SCAN Health Plan} % Organization
    {Long Beach, CA, U.S.} % Location
    {Nov. 2023 - Jun. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Owned inventory, imaging, and disposition workflows; kept CMDB accuracy and chain-of-custody for audits.}
        \item {Scripted data pulls and bulk updates for asset hygiene; aligned records with security and finance controls.}
        \item {Coordinated with vendors and internal teams on RMA, warranty, and secure disposal requirements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Technician (Consulting)} % Job title
    {Robert Half — multiple client sites} % Organization
    {Los Angeles, CA, U.S.} % Location
    {Aug. 2021 - Jan. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Executed workforce augmentation, site moves, deployments, and break/fix under client playbooks and change windows across diverse environments.}
        \item {Performed imaging, upgrades, and network connectivity triage; escalated using standard incident and outage procedures.}
        \item {Adapted quickly to each org’s standards and toolsets; collaborated with facilities, vendors, and security when required.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Help Desk I} % Job title
    {GT's Living Foods} % Organization
    {Commerce, CA, U.S.} % Location
    {Sep. 2020 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported industrial IT: Zebra scanners/printers, handhelds, and ERP users on the production floor across multiple company industrial facilities in the Commerce area.}
        \item {Performed testing, troubleshooting, heat mapping and validation of industrial Wi-Fi coverage to ensure stable operations.}
        \item {Administered Avigilon video and smart-card access; coordinated camera/reader adds and user changes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Physical Security Program Manager} % Job title
    {U.S. Navy} % Organization
    {Okianwa, Japan \& San Diego, CA, U.S.} % Location
    {Jul. 2014 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Established Physical Security program for regional bases and led facility physical-security inspections and corrective-action tracking under DoD AT/FP and NISPOM guidance. Performed and oversaw reporting of DoD Physical Security assessments to the Pentagon.}
        \item {Coordinated with IT, facilities, and tenant commands on access control, intrusion detection, network expansion, and CCTV implementation.}
        \item {Enforced SCIF classified-area compliance; familiarity with UL 2050 monitoring and ICD 705 inspection expectations.}
        \item {Managed security clearances and foreign national access using JPAS/DISS in compliance with DoD 5200.2-R and NISPOM requirements.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
