%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
% *** ChatGPT Suggested entry
\tightsection
\cvsection{Extracurricular Activity}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
%\textbf{Groups}
\begin{cventries}
%---------------------------------------------------------
  \tightsection

  
 \textbf{Professional Memberships} 
  
  \cventry
    {Volunteer DevOps Security Engineer} % Affiliation/role
    {Hack for LA(Los Angeles chapter of Code for America)} % Organization/group
    {Los Angeles, CA} % Location
    {Jun. 2025 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
         \item {Volunteer DevOps Security engineer for civic tech group “Hack for LA”.}
        \item {Carried out full IAM audit, reviewing credentialing, privilege management, account administration processes, logging, monitoring, back-end and front-end security policy, AWS security configuration, Terraform posture, and Infrastructure-as-Code(IaC) best practices in line with industry standards).}
        \item {Manages CI/CD security policy in Terraform / AWS environment.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Onboarded Volunteer Analyst} % Affiliation/role
    {Arachne Digital - Open-Source Cyber Threat Intelligence} % Organization/group
    {Remote, International} % Location
    {2025 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Engage with an open-source cyber threat intelligence community focused on mapping threat reports to frameworks such as MITRE ATT\&CK\textsuperscript{\textregistered} and DISARM.}
        \item {Build skills in threat-informed defense, OSINT-driven investigations, and structured CTI reporting in support of security operations and disinformation defense.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Null Space Labs} % Organization/group
    {Glendale, CA} % Location
    {2021 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Hardware hacking, RF, and tooling meetups; shared lab projects.}
        \item {Attended multiple instructor-led classes in locks \& lockpicking, gaining hands-on experience with lock function, industry offerings, and exploitation.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {Homeland Security Information Network} % Organization/group
    {Remote, United States} % Location
    {2025-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Vetted participant in DHS’s Sensitive But Unclassified (SBU) information-sharing environment supporting homeland security and critical infrastructure stakeholders.}
        \item {Leverages official threat advisories and situational awareness products to inform converged physical–cyber security perspectives and risk assessments.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Member} % Affiliation/role
    {FBI InfraGard} % Organization/group
    {Remote, United States} % Location
    {2025-Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Participates in trusted information-sharing on threats to U.S. critical infrastructure sectors.}
        \item {Engages with public–private partnership initiatives to align physical security, cybersecurity, and incident response practices with federal guidance.}
      \end{cvitems}
    }

%---------------------------------------------------------

\textbf{Events}


  \cventry
    {Attendee}
    {Google SF Fleet Week Veterans' Invitational}
    {San Francisco, CA}
    {Oct. 2025}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Invited for Google Fleet Week 2025 Veterans' Career conference, comprising networking, skill building, and research.}
      \end{cvitems}
      }
  \cventry
    {Attendee}
    {AWS Summit: Los Angeles}
    {Los Angeles, CA}
    {Sep. 2025}
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Attended keynotes, instructor-led hands-on training, briefs involving new offerings, and networked with AWS-oriented vendors.}
      \end{cvitems}
      }
      
\textbf{Projects}


\cventry
    {Designer \& Operator}
    {Personal Homelab Buildout}
    {Los Angeles, CA}
    {2023 - Present}
    {
      \begin{cvitems}
        \item {Proxmox, VPN, Docker, dashboards, VMs, VPN and monitoring. }
            \begin{itemize}
                \item Integrated with personal AWS and Azure tenants for hybrid cloud environment education and lab study.
                \item Docker VM with Portainer, Homarr dashboard and FreshRSS.
                \item Modified Trace Labs OSINT VM with extended toolset
                \item pfSense/WireGuard VPN gateway for secure remote access.
                \item Samba file share for centralized storage, backups and cross-device access in the homelab.
                \item Internal custom certificate authority (CA) to issue TLS certificates for lab services.
                \item GitHub-integrated DevOps environment (VS Code, Git, CI/CD pipelines) for developing and testing homelab services.
            \end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
%  \cventry
%    {Member} % Affiliation/role
%    {VetSec} % Organization/group
%    {National} % Location
%    {May. 2025 - Present} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of experience/contributions/knowledge
%        \item {Veterans cybersecurity community, mentorship, education, events and job-search support.}
%      \end{cvitems}
%    }
%---------------------------------------------------------
\end{cventries}
