%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
% *** ChatGPT Suggested entry
\tightsection
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \tightsection
  \cventry
    {IT OPERATIONS SPECIALIST} % Job title
    {SCAN Health Plan} % Organization
    {Long Beach, CA} % Location
    {Jul. 2024 - May. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Administered Azure hybrid-cloud environment for 1,500 users and 2,000 devices across four sites, supporting Exchange, Intune, Entra, SharePoint, OneDrive, and GlobalProtect VPN.}
        \item {Automated user life cycle and administration tasks with PowerShell/Python and AAD/Exchange APIs; reduced account management manual overhead by 40\%.}
%        \item {Built asset and patch reports from Lansweeper asset management database; improved cross-team visibility for audits and change reviews.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {ASSET MANAGEMENT TECHNICIAN} % Job title
    {SCAN Health Plan} % Organization
    {Long Beach, CA} % Location
   {Nov. 2023 - Jun. 2025} % Date(s)
   {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed 2,000 endpoints via Intune and SCCM, performing OS deployments, hardware repair, and mobile device enrollment.}
        \item {Authored Python script for LanSweeper's API to automate asset data collection, reducing manual workload by 98\%.}
        \item {Enforced encryption and patch compliance using BitLocker and Absolute MDM.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Audio/Visual Network Engineer} % Job title
    {Higher9 Productions} % Organization
    {Los Angeles, CA} % Location
    {Aug. 2022 - Nov. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, upgraded and deployed live event network infrastructure using Dante, Lake Controllers, and Danley systems; configured switches, PoE, and specialized AV hardware for dynamic productions.}
        \item {Led an 8-person team to deliver zero-downtime operations and 100\% event reliability across concurrent venues.}
        \item {Maintained 100\% quality of delivery, installation, expert troubleshooting and maximal up-time in the face of new environments daily and crowd-originating network interruptions.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Consultant} % Job title
    {Robert Half — multiple clients} % Organization
    {Los Angeles, CA} % Location
    {Feb. 2021 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Executed workforce augmentation, site moves, deployments, and break/fix under client playbooks and change windows across diverse environments.}
        \item {Performed imaging, upgrades, and network connectivity triage; escalated using standard incident and outage procedures.}
        \item {Adapted quickly to each org’s standards and tool sets; collaborated with facilities, vendors, and security when required.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {IT Help Desk I} % Job title
    {GT's Living Foods} % Organization
    {Commerce, CA} % Location
    {Feb. 2020 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Supported more than 1500 industrial users across four facilities, comprised corporate and industrial environments and applications, administering Cisco Meraki wireless mobile device management to monitor and support Microsoft Surface and personal mobile devices.}
        \item {Co-led Avigilon access system upgrade, reducing technical vulnerabilities by 50\%.}
        \item {Improved warehouse wireless reliability by 95\% through network remapping and hardware redeployment.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Physical Security Program Manager} % Job title
    {U.S. Navy} % Organization
    {Okianwa, Japan \& San Diego, CA} % Location
    {Jul. 2014 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Oversaw converged security compliance and protection of facilities, assets, and equipment valued at over \$150 million across six Navy and joint bases}
        \item {Overhauled and managed Anti-Terrorism/Physical Security program for ~300 facilities involving compliance audits, SCIF classified‑area management, vulnerability assessments, CCTV implementation, asset protection, risk remediation, and reporting to Pentagon.}
        \item {Enforced SCIF classified-area compliance; familiarity with UL 2050 monitoring and ICD 705 inspection expectations.}
        \item {Coordinated with NCIS to tailor base security posture in response to threat intelligence data.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
